### 2018-01-10 master/paper.tex
Add TECS adapter

@@

>>>>

\subsection{TECS adapter}
\label{sec:TECSAdapter}

TINET+TECS supports legacy codes because TECS supports {\it Adapter} functionality, which enables to calling a function in TECS from existing C codes.
The adapter is implemented between C codes and a TECS component and links a C function to a TECS function as shown in Fig. \ref{fig:TECSAdapter}.
In TINET+TECS, when an application calls an API such as {\it tcp\_snd\_dat}, the adapter component calls a function of tTCPCEP such as {\it eAPI\_sendData}.
Note that {\it tcp\_snd\_dat} is defined under the name {\it eAPI\_sendData} in TINET+TECS.
The adapter wraps the APIs used in the existing applications into TECS functions, enabling software developers to utilize an existing TCP/IP application via the adapter.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/TECSAdapter.pdf}
    \caption{TECS adapter}
    \label{fig:TECSAdapter}
\end{figure}

Since existing communication programs are supported, a communication task can be applied without porting, and other tasks can be developed with mruby program.

@@

\subsection{Adapter overhead}

The API execution time when using an adapter such as {\it tcp\_snd\_dat/eAPI\_sendData} was used to analyze the overhead of the TECS adapter supporting existing applications.
As shown in Fig. \ref{fig:EvaluationOfAdapter}, the overhead of the TECS adapter is very small because the adapter only passes parameters from C codes to TECS components; thus, the TECS adapter overhead does not affect the system.

\begin{figure}[t]
    \centering
    \includegraphics[width=10cm,clip]{figure/EvaluationOfAdapter.pdf}
    \caption{Execution times in two cases (without/with TECS adapter)}
    \label{fig:EvaluationOfAdapter}
\end{figure}
